Cycles of the logistic map

### 2013-05-03 doc/pc-ijbc.tex
add references, update webpages

To simplify the calculation, we first change variables \cite{saha} as
%
%\begin{equation}
\[
    x^{\mathrm{new}} \equiv r(x^{\mathrm{old}} - 1/2),
    \quad R \equiv r(r-2)/4,
\]
%\label{eq:chvars}
%\end{equation}
%
and rewrite the map, in terms of $x^{\mathrm{new}}$, as
%
\begin{equation}
  x_{k+1} = f(x_k) \equiv R - {x_k}^2.
  %\tag{$\ref{eq:logmap}'$}
\label{eq:logmaps}
\end{equation}
%
%\refeq{logmaps} simplifies \refeq{logmap} as $x_k$ now only occurs once.
%
We will solve the cycle boundaries as zeros of some polynomials of $R$,
and the corresponding polynomials for $r$ can be obtained by $R \rightarrow r(r-2)/4$.
%
%the numerical $r$ values can always be obtained from $r = 1 + \sqrt{1 + 4R}$.
%

@@

A polynomial is cyclic if it is invariant
  under the cycling of variables
  $x_1 \rightarrow x_2, x_2 \rightarrow x_3,
  \ldots, x_n \rightarrow x_1$,
  e.g., $a = x_1 x_2 + x_2 x_3 + x_3 x_4 + x_4 x_1$
  and $b = x_1 x_3 + x_2 x_4$ (for $n = 4$).
%
Note that a cyclic polynomial is not necessarily symmetric
  (i.e., invariant under the exchange of any two $x_k$ and $x_{j}$),
  e.g., $a$ and $b$ are not symmetric,
  but $a + b$ is.

@@

Cyclic polynomials
  generated from monomials of unit coefficient
  (such as $a$ and $b$, but not $a + b$ in the above example)
  can be labeled as follows.
We write the monomial generator as
  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
  and form a sequence $p$ of indices with
  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s.
The sequence $p$ serves as the label of the cyclic polynomial $C_p(\vxn{n})$,
  where $\vxn{n} \equiv \{x_1, \ldots, x_n\}$
(we will, however, drop the superscript ``$^{(n)}$'' or
  even the argument ``$(\vxn{n})$'' entirely when it is clear).
For example,
  $C_{12}(\vx)  = x_1 x_2 + x_2 x_3 + \dots + x_n x_1$ and
  $C_{112}(\vx) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
%The cycle length $n$ is omitted for convenience.
%  for we will mostly work with a fixed $n$ at a time.
In case the cyclic polynomial has several generators,
%  e.g., both $x_1 x_2$ and $x_2 x_3$ are generators of $C_{12}(\vx)$
%   (assuming $n \ge 3$),
  we pick the one with the smallest $p$
  in the sense of lexicographic order,
  e.g., we choose $x_1 x_2$ instead of $x_2 x_3$ for $C_{12}(\vx)$
  because $12 < 23$ ($n \ge 3$).
Finally, we add $C_0(\vx) \equiv 1$ for completeness.
%
%
%

@@

\begin{remark}
  Generally, the algorithm can trace a contour of marginal stability of $R$
  in the complex plane
  for complex cycles (i.e., complex $R$ and $\vx$)
  if $\lambda$ is set to $\exp(i\theta)$ with $\theta \in [0, 2\pi]$.
  The region enclosed by the contour corresponds to a bulb in the inverted Mandelbrot set
  (the correspondence follows from the transformation $z_k = -x_k, c = -R$, which
  reduces \refeq{logmaps} to the quadratic map $z_{k+1} = c + {z_k}^2$
  used in the Mandelbrot set),
  see ref. \cite{stephenson}. % and \reffig{logbulb}.
\end{remark}

@@

For $n = 1$, we have two square-free cyclic polynomials
  $C_0 = 1$ and $C_1 = x_1$;
  and $\Lambda = -2 \, x_1$
Thus,
$\Lambda \, C_0 = -2 \, x_1$,
$\Lambda \, C_1 = -2 \, x_1^2 = -2 \, R + 2  \, x_1$,
and
\[
  \Lambda
  \left( \begin{array}{c}
  C_0 \\
  C_1
  \end{array} \right)
  =
  \left( \begin{array}{cc}
  0     & -2 \\
  -2R   &  2
  \end{array}\right)
  \left( \begin{array}{c}
  C_0 \\
  C_1
  \end{array} \right).
\]
With $\Lambda \rightarrow \lambda$, the characteristic equation (\ref{eq:xr}) reads
\begin{equation}
0=  \left| \begin{array}{cc}
  \lambda     & 2          \\
  2 R         & \lambda - 2
  \end{array} \right| = -4R - 2\lambda + \lambda^2.
  \tag{\ref{eq:xr}-1}
\label{eq:xr1}
\end{equation}
Thus, $R = (\lambda^2 -2\lambda)/4$;
  and the fixed point begins at $R_a = -1/4$ ($\lambda = +1$),
  and becomes unstable at $R_b = 3/4$ ($\lambda = -1$).

@@

The $n = 3$ case is nontrivial and has sparked several different
  elementary derivations \cite{saha, bechhoefer, gordon, burm, zhang}.
For the current algorithm,
the cyclic polynomials are
$C_0 = 1$,
$C_1 = x_1 + x_2 + x_3$,
$C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$,
$C_{123} = x_1 x_2 x_3$,
and
$\Lambda = -8 \, C_{123}$.
%
The square-free reduction yields
%
\footnotesize
\begin{align*}
\Lambda
\left( \begin{array}{c}
  C_0 \\
  C_1 \\
  C_{12} \\
  C_{123}
\end{array} \right)
=
\left( \begin{array}{cccc}
 0            & 0                 & 0               & -8 \\
 -24 R        & 8(R+1)            & -8R             & 0 \\
 24 R^2       & -8R(R+2)          & 8(R+1)          & 0 \\
 -8R^3        & 8R^2              & -8R             & 8
  \end{array} \right)
\left( \begin{array}{c}
  C_0 \\
  C_1 \\
  C_{12} \\
  C_{123}
\end{array} \right),
\end{align*}
\normalsize
%
%
%
and \refeq{xr} reads:
\begin{align}
  0
&= -\big[
  64R^3 - 128 R^2 - 8 (\lambda - 8) R - (\lambda -8)^2
  \big] \notag \\
&\qquad
  \big(
  \lambda^2 - 8\lambda - 24 R\lambda - 64 R^3
  \big).
  \tag{\ref{eq:xr}-3}
\label{eq:xr3}
\end{align}
%
Using the first factor, we find at the onset point
  $\lambda = 1$,
  $\left(
  R-\frac74
  \right)
  \left(
  R^2-\frac14 R + \frac{7}{16}
  \right)=0$
  and its only real solution is $R_a = 7/4$ ($r_a = 1+\sqrt 8$).
%
At the bifurcation point $\lambda = -1$,
  the equation $R^3-2R^2 + \frac{9}{8} R -\frac{81}{64}=0$
  yields
  $R_b = \frac14
      \left(
      \frac{8}{3} +
        \sqrt[3]{\frac{1915}{54} - \frac52\sqrt{201}}
       +\sqrt[3]{\frac{1915}{54} + \frac52\sqrt{201}}
      \right)$,
whose corresponding $r = 1+\sqrt{1+4R}$
is identical to that in ref. \cite{gordon, burm}.
%

The $n = 4$ case was previously used
as a test of several algorithms
\cite{stephenson, bailey1, kk1, bailey2, lewis}.
%$C_0 = 1$,
%$C_1 = x_1 + \cdots + x_4$,
%$C_{12} = x_1 x_2 + \cdots + x_4 x_1$,
%$C_{13} = x_1 x_3 + x_2 x_4$,
%$C_{123} = x_1 x_2 x_3 + \cdots + x_4 x_1 x_2$,
%$C_{1234} = x_1 x_2 x_3 x_4$,
%and
%$\Lambda = 16 \, C_{1234}$.
%
Here, we only list the final characteristic equation \eqref{eq:xr}
after the square reduction (with six square-free cyclic polynomials):
%
\footnotesize
\begin{align}
0
%& = \left|
%\begin{array}{cccccc}
% \lambda  & 0               & 0                 & 0     & 0     & -16 \\
% 64 R     & \lambda-16(R+1) & 16 R              & 0     & -16R  & 0 \\
% -64 R^2  & 16R(R+2)        & \lambda-16(R^2+1) & -32 R & 16R   & 0 \\
% -32 R^2  & 16R(R+1)        & -16R              & \lambda-16(R^2+1)  & 0 & 0 \\
% 64 R^3   & -16R^2(R+3)     & 16R(R+2)        & 32 R (R+1)       & \lambda-16(R+1) & 0 \\
% -16R^4   & 16R^3           & - 16R^2           & -16R^2            & 16R & \lambda - 16
%\end{array}
%\right | \nonumber  \\
& =
    \big[
    4096 R^6-12288 R^5 + 256 (\lambda + 48) (R^4- R^3) \notag \\
& \quad
    -16 (\lambda + 32)(\lambda - 16) R^2
      -(\lambda - 16)^3 \big] \notag \\
& \quad
    \big[ 16 (R-1)^2 - \lambda \big]
 \, \big[(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda \big],
  \tag{\ref{eq:xr}-4}
\label{eq:xr4}
\end{align}
\normalsize
%
%
%
The first (sextic) factor, responsible for the 4-cycle,
can be factorized as
$ (
    4R - 5
  )
\, \big[
  (4R + 1)^2 + 4
  \big]
\, \big[
  (4R - 3)^3 - 108
  \big] =0$
at the onset point $\lambda = 1$.
%
%
%
It has two real roots:
$R_a' = 5/4$
\big($r_a' = 1+\sqrt{6} \approx 3.4495$\big)
for the cycle from period-doubling the 2-cycle
  \big[compare \reffigs{cobweb}(b) and (d)\big],
and
$R_a = (3+\sqrt[3]{108})/4$
\big($r_a = 1+\sqrt{4+\sqrt[3]{108}} \approx 3.9601$\big)
for an original cycle \big[\reffig{cobweb}(e)\big].
%
At the bifurcation point ($\lambda = -1$), we have
$4096 R^6 - 12288 R^5 + 12032 (R^4 - R^3)
  + 8432 R^2 + 4913 = 0$,
which upon $R \rightarrow r(r-2)/4$ yields the same polynomial
obtained previously
\cite{bailey1, kk1, bailey2, lewis}.
%
The only two positive roots $r_b \approx 3.9608$
and $r_b' \approx 3.5441$ of the sextic equation
correspond to $r_a$ and $r_a'$ respectively.
%
Since the 4-cycle problem were tackled mainly on computers
  in the previous studies,
  we also supply a compact elementary derivation
  in the Appendix.

@@

\begin{table}[h]\footnotesize
  %\caption{
  \tbl{
  Smallest positive $r$ at the onset and bifurcation points
  of the $n$-cycles of the logistic map.
  }
%\begin{center}
{
\begin{tabular}{llll}
%\begin{tabularx}{\linewidth}{
%  >{\hsize=0.5\hsize\centering\arraybackslash}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
%}
\hline
  $n^\dagger$
& Onset$^\ddagger$
& Bifurcation$^\ddagger$
& \#$^*$ \\
\hline
$1$     & $1.0000000000_1$      &  $3.0000000000_1$       & 1   \\
$2'$    & $3.0000000000_1$      &  $3.4494897428_1$       & 1   \\
$3$     & $3.8284271247_1$      &  $3.8414990075_3$       & 1   \\
$4$     & $3.9601018827_3$      &  $3.9607686524_6$       & 1   \\
$4''$   & $3.4494897428_1$      &  $3.5440903596_6$       & 1   \\
$5$     & $3.7381723753_{11}$   &  $3.7411207566_{15}$    & 3   \\
$6$     & $3.6265531617_{20}$   &  $3.6303887000_{27}$    & 4   \\
$6'$    & $3.8414990075_{3}$    &  $3.8476106612_{27}$    & 1   \\
$7$     & $3.7016407642_{57}$   &  $3.7021549282_{63}$    & 9   \\
$8$     & $3.6621089132_{108}$  &  $3.6624407072_{120}$   & 14  \\
$8'$    & $3.9607686524_{6}$    &  $3.9610986335_{120}$   & 1   \\
$8'''$  & $3.5440903596_{6}$    &  $3.5644072661_{120}$   & 1   \\
$9$     & $3.6871968733_{240}$  &  $3.6872742105_{252}$   & 28  \\
$10$    & $3.6052080669_{472}$  &  $3.6059169323_{495}$   & 48  \\
$10'$   & $3.7411207566_{15}$   &  $3.7425706462_{495}$   & 3   \\
$11$    & $3.6817160194_{1013}$ &  $3.6817266457_{1023}$  & 93  \\
$12$    & $3.5820230011_{1959}$ &  $3.5828117795_{2010}$  & 165 \\
$12'$   & $3.6303887000_{27}$   &  $3.6321857392_{2010}$  & 4   \\
$12''$  & $3.8476106612_{27}$   &  $3.8490363152_{2010}$  & 1   \\
$13$    & $3.6797024578_{4083}$ &  $3.6797038498_{4095}$  & 315 \\
\hline
\multicolumn{4}{p{\linewidth}}{
$^\dagger$
  $\,'$, $\,''$, or $\,'''$ means
    that the cycle is undergoing
    the first, second, or third successive period-doubling, respectively.
} \\
\multicolumn{4}{p{\linewidth}}{
$^\ddagger$
  The subscripts are the degrees of the corresponding minimal polynomial
    of $R = r(r-2)/4$.
} \\
\multicolumn{4}{p{\linewidth}}{
$^*$
  The number of similar cycles.
} \\
\hline
%\end{tabularx}
\end{tabular}
\label{tab:rval}
}
%\end{center}
\end{table}

@@

The characteristic polynomial $A_n\Rlam$ in \refeq{xr}
  is derived for the fixed points of $f^n$.
Thus, it encompasses not only the $n$-cycles,
  but also cycles of shorter periods $d$ ($d|n$).
%
We can remove the contributions from the shorter cycles by the following theorem.

>>>>

To simplify the calculation, we first change variables \cite{mandelbrot, brown1, brown2, saha} as
%
%\begin{equation}
\[
    x^{\mathrm{new}} \equiv r(x^{\mathrm{old}} - 1/2),
    \quad R \equiv r(r-2)/4,
\]
%\label{eq:chvars}
%\end{equation}
%
and rewrite the map, in terms of $x^{\mathrm{new}}$, as
%
\begin{equation}
  x_{k+1} = f(x_k) \equiv R - {x_k}^2.
  %\tag{$\ref{eq:logmap}'$}
\label{eq:logmaps}
\end{equation}
%
%\refeq{logmaps} simplifies \refeq{logmap} as $x_k$ now only occurs once.
%
We will solve the cycle boundaries as zeros of some polynomials of $R$,
and the corresponding polynomials for $r$ can be obtained by $R \rightarrow r(r-2)/4$.
%
%the numerical $r$ values can always be obtained from $r = 1 + \sqrt{1 + 4R}$.
%

@@

A cyclic polynomial is an invariant
  under the cycling of variables
  $x_1 \rightarrow x_2, x_2 \rightarrow x_3,
  \ldots, x_n \rightarrow x_1$,
  e.g., $a = x_1 x_2 + x_2 x_3 + x_3 x_4 + x_4 x_1$
  and $b = x_1 x_3 + x_2 x_4$ (for $n = 4$).
%
It is, however, not necessarily symmetric
  (i.e., invariant under the exchange of any two $x_k$ and $x_{j}$),
  e.g., $a$ and $b$ are not symmetric,
  but $a + b$ is.

@@

Cyclic polynomials
  generated from monomials of unit coefficient
  (such as $a$ and $b$, but not $a + b$ in the above example)
  can be labeled as follows.
We write the monomial generator as
  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
  and form a sequence $p$ of indices with
  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s.
The sequence $p$ serves as the label of the cyclic polynomial $C_p(\vxn{n})$,
  where $\vxn{n} \equiv \{x_1, \ldots, x_n\}$
[we will, however, drop the superscript ``$^{(n)}$'' or
  even the argument ``$(\vxn{n})$'' entirely when it is clear].
For example,
  $C_{12}(\vx)  = x_1 x_2 + x_2 x_3 + \dots + x_n x_1$ and
  $C_{112}(\vx) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
%The cycle length $n$ is omitted for convenience.
%  for we will mostly work with a fixed $n$ at a time.
In case the cyclic polynomial has several generators,
%  e.g., both $x_1 x_2$ and $x_2 x_3$ are generators of $C_{12}(\vx)$
%   (assuming $n \ge 3$),
  we pick the one with the smallest $p$
  in the sense of lexicographic order,
  e.g., we choose $x_1 x_2$ instead of $x_2 x_3$ for $C_{12}(\vx)$
  because $12 < 23$ ($n \ge 3$).
Finally, we add $C_0(\vx) \equiv 1$ for completeness.
%
%
%

@@

\begin{remark}
  Generally, the algorithm can trace a contour of marginal stability of $R$
  in the complex plane
  for complex cycles $\vx$
  if $\lambda$ is set to $\exp(i\theta)$ with $\theta \in [0, 2\pi]$.
  The region enclosed by the contour corresponds to
    a bulb in the inverted Mandelbrot set
  (the correspondence follows from the transformation $z_k = -x_k, c = -R$, which
  reduces \refeq{logmaps} to the quadratic map $z_{k+1} = c + {z_k}^2$
  used in the Mandelbrot set \cite{mandelbrot}),
  see ref. \cite{stephenson2, stephenson3}. % and \reffig{logbulb}.
\end{remark}

@@

For $n = 1$, we have
  $C_0 = 1$, $C_1 = x_1$, $\Lambda = -2 \, x_1$, and
%Thus,
%$\Lambda \, C_0 = -2 \, x_1$,
%$\Lambda \, C_1 = -2 \, x_1^2 = -2 \, R + 2  \, x_1$,
%and
\[
  \Lambda
  \left( \begin{array}{c}
  C_0 \\
  C_1
  \end{array} \right)
  =
  \left( \begin{array}{cc}
  0     & -2 \\
  -2R   &  2
  \end{array}\right)
  \left( \begin{array}{c}
  C_0 \\
  C_1
  \end{array} \right).
\]
With $\Lambda \rightarrow \lambda$, the characteristic equation (\ref{eq:xr}) reads
\begin{equation}
0=  \left| \begin{array}{cc}
  \lambda     & 2          \\
  2 R         & \lambda - 2
  \end{array} \right| = -4R - 2\lambda + \lambda^2.
  \tag{\ref{eq:xr}-1}
\label{eq:xr1}
\end{equation}
Thus, $R = (\lambda^2 -2\lambda)/4$;
  and the fixed point begins at $R_a = -1/4$ ($\lambda = +1$),
  and becomes unstable at $R_b = 3/4$ ($\lambda = -1$).

@@

The $n = 3$ case is nontrivial and has sparked several different
  elementary derivations \cite{brown1, saha, bechhoefer, gordon, burm, zhang}.
For the current algorithm,
%the cyclic polynomials are
%$C_0 = 1$,
%$C_1 = x_1 + x_2 + x_3$,
%$C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$,
%$C_{123} = x_1 x_2 x_3$,
%and
$\Lambda = -8 \, C_{123}$,
%
and the square-free reduction yields
%
\begin{small}
\begin{align*}
\Lambda
\left( \begin{array}{c}
  C_0 \\
  C_1 \\
  C_{12} \\
  C_{123}
\end{array} \right)
=
\left( \begin{array}{cccc}
 0            & 0                 & 0               & -8 \\
 -24 R        & 8(R+1)            & -8R             & 0 \\
 24 R^2       & -8R(R+2)          & 8(R+1)          & 0 \\
 -8R^3        & 8R^2              & -8R             & 8
  \end{array} \right)
\left( \begin{array}{c}
  C_0 \\
  C_1 \\
  C_{12} \\
  C_{123}
\end{array} \right),
\end{align*}
\end{small}
%
%
%
and \refeq{xr} reads:
\begin{align}
  0
&= -\big[
  64R^3 - 128 R^2 - 8 (\lambda - 8) R - (\lambda -8)^2
  \big] \notag \\
&\qquad
  \big(
  \lambda^2 - 8\lambda - 24 R\lambda - 64 R^3
  \big).
  \tag{\ref{eq:xr}-3}
\label{eq:xr3}
\end{align}
%
Using the first factor, we find at the onset point
  $\lambda = 1$,
  $\left(
  R-\frac74
  \right)
  \left(
  R^2-\frac14 R + \frac{7}{16}
  \right)=0$
  and its only real solution is $R_a = 7/4$ ($r_a = 1+\sqrt 8$).
%
At the bifurcation point $\lambda = -1$,
  the equation $R^3-2R^2 + \frac{9}{8} R -\frac{81}{64}=0$
  yields
  $R_b = \frac14
      \left(
      \frac{8}{3} +
        \sqrt[3]{\frac{1915}{54} - \frac52\sqrt{201}}
       +\sqrt[3]{\frac{1915}{54} + \frac52\sqrt{201}}
      \right)$,
whose corresponding $r = 1+\sqrt{1+4R}$
is identical to that in ref. \cite{gordon, burm}.
%

For the $n = 4$ case
\cite{brown1, stephenson1, stephenson3, bailey, kk1, lewis},
%$C_0 = 1$,
%$C_1 = x_1 + \cdots + x_4$,
%$C_{12} = x_1 x_2 + \cdots + x_4 x_1$,
%$C_{13} = x_1 x_3 + x_2 x_4$,
%$C_{123} = x_1 x_2 x_3 + \cdots + x_4 x_1 x_2$,
%$C_{1234} = x_1 x_2 x_3 x_4$,
%and
%$\Lambda = 16 \, C_{1234}$.
%
we only list the final characteristic equation \eqref{eq:xr}
after the square reduction (with six square-free cyclic polynomials):
%
\begin{small}
\begin{align}
0
%& = \left|
%\begin{array}{cccccc}
% \lambda  & 0               & 0                 & 0     & 0     & -16 \\
% 64 R     & \lambda-16(R+1) & 16 R              & 0     & -16R  & 0 \\
% -64 R^2  & 16R(R+2)        & \lambda-16(R^2+1) & -32 R & 16R   & 0 \\
% -32 R^2  & 16R(R+1)        & -16R              & \lambda-16(R^2+1)  & 0 & 0 \\
% 64 R^3   & -16R^2(R+3)     & 16R(R+2)        & 32 R (R+1)       & \lambda-16(R+1) & 0 \\
% -16R^4   & 16R^3           & - 16R^2           & -16R^2            & 16R & \lambda - 16
%\end{array}
%\right | \nonumber  \\
& =
    \big[
    4096 R^6-12288 R^5 + 256 (\lambda + 48) (R^4- R^3) \notag \\
& \quad
    -16 (\lambda + 32)(\lambda - 16) R^2
      -(\lambda - 16)^3 \big] \notag \\
& \quad
    \big[ 16 (R-1)^2 - \lambda \big]
 \, \big[(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda \big],
  \tag{\ref{eq:xr}-4}
\label{eq:xr4}
\end{align}
\end{small}
%
%
%
The first (sextic) factor, responsible for the 4-cycle,
can be factorized as
$ (
    4R - 5
  )
\, \big[
  (4R + 1)^2 + 4
  \big]
\, \big[
  (4R - 3)^3 - 108
  \big] =0$
at the onset point $\lambda = 1$.
%
%
%
It has two real roots:
$R_a' = 5/4$
\big($r_a' = 1+\sqrt{6} \approx 3.4495$\big)
for the cycle from period-doubling the 2-cycle
  \big[compare \reffigs{cobweb}(b) and (d)\big],
and
$R_a = (3+\sqrt[3]{108})/4$
\big($r_a = 1+\sqrt{4+\sqrt[3]{108}} \approx 3.9601$\big)
for an original cycle \big[\reffig{cobweb}(e)\big].
%
At the bifurcation point ($\lambda = -1$), we have
$4096 R^6 - 12288 R^5 + 12032 (R^4 - R^3)
  + 8432 R^2 + 4913 = 0$,
which upon $R \rightarrow r(r-2)/4$ yields the same polynomial
obtained previously
\cite{bailey, kk1, lewis}.
%
The only two positive roots $r_b \approx 3.9608$
and $r_b' \approx 3.5441$ of the sextic equation
correspond to $r_a$ and $r_a'$ respectively.
%
%Since the 4-cycle problem were tackled mainly on computers
%  in the previous studies,
%  we also supply a compact elementary derivation
%  in the Appendix.

@@

\begin{table}[h]\footnotesize
  \tbl{
  Smallest positive $r$ at the onset and bifurcation points
  of the $n$-cycles of the logistic map.
  }
{
\begin{tabular}{llll}
%\begin{tabularx}{\linewidth}{
%  >{\hsize=0.5\hsize\centering\arraybackslash}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
%}
\hline
  $n^\dagger$
& Onset$^\ddagger$
& Bifurcation$^\ddagger$
& \#$^*$ \\
\hline
$1$     & $1.0000000000_1$      &  $3.0000000000_1$       & 1   \\
$2'$    & $3.0000000000_1$      &  $3.4494897428_1$       & 1   \\
$3$     & $3.8284271247_1$      &  $3.8414990075_3$       & 1   \\
$4$     & $3.9601018827_3$      &  $3.9607686524_6$       & 1   \\
$4''$   & $3.4494897428_1$      &  $3.5440903596_6$       & 1   \\
$5$     & $3.7381723753_{11}$   &  $3.7411207566_{15}$    & 3   \\
$6$     & $3.6265531617_{20}$   &  $3.6303887000_{27}$    & 4   \\
$6'$    & $3.8414990075_{3}$    &  $3.8476106612_{27}$    & 1   \\
$7$     & $3.7016407642_{57}$   &  $3.7021549282_{63}$    & 9   \\
$8$     & $3.6621089132_{108}$  &  $3.6624407072_{120}$   & 14  \\
$8'$    & $3.9607686524_{6}$    &  $3.9610986335_{120}$   & 1   \\
$8'''$  & $3.5440903596_{6}$    &  $3.5644072661_{120}$   & 1   \\
$9$     & $3.6871968733_{240}$  &  $3.6872742105_{252}$   & 28  \\
$10$    & $3.6052080669_{472}$  &  $3.6059169323_{495}$   & 48  \\
$10'$   & $3.7411207566_{15}$   &  $3.7425706462_{495}$   & 3   \\
$11$    & $3.6817160194_{1013}$ &  $3.6817266457_{1023}$  & 93  \\
$12$    & $3.5820230011_{1959}$ &  $3.5828117795_{2010}$  & 165 \\
$12'$   & $3.6303887000_{27}$   &  $3.6321857392_{2010}$  & 4   \\
$12''$  & $3.8476106612_{27}$   &  $3.8490363152_{2010}$  & 1   \\
$13$    & $3.6797024578_{4083}$ &  $3.6797038498_{4095}$  & 315 \\
\hline
\multicolumn{4}{p{\linewidth}}{
$^\dagger$
  $\,'$, $\,''$, or $\,'''$ means
    that the cycle is undergoing
    the first, second, or third successive period-doubling, respectively.
} \\
\multicolumn{4}{p{\linewidth}}{
$^\ddagger$
  The subscripts are the degrees of the corresponding minimal polynomial
    of $R = r(r-2)/4$.
} \\
\multicolumn{4}{p{\linewidth}}{
$^*$
  The number of similar cycles.
} \\
\hline
%\end{tabularx}
\end{tabular}
\label{tab:rval}
}
\end{table}

@@

The characteristic polynomial $A_n\Rlam$ in \refeq{xr}
  is derived for the fixed points of $f^n$.
Thus, it represents not only the $n$-cycles,
  but also cycles of shorter periods $d$ ($d|n$).
%
We can remove the contributions from the shorter cycles by the following theorem.

\begin{theorem}
  The minimal polynomial $P_n\Rlam$ of all $n$-cycles
  is a factor of the characteristic polynomial $A_n\Rlam$,
  and can be computed as
  \begin{equation}
    P_n\Rlam
    = \prod_{cd = n} B_{d,c}\Rlam^{\mu(c)},
  \label{eq:primfac}
  \end{equation}
where
  $B_{d, c}\Rlam \equiv \prod_{k=1}^c A_{d}(R, e^{2k\pi i/c} \lambda^{1/c})$,
  $\lambda^{1/c}$ is a complex $c$th root of $\lambda$,
  and $\mu(c)$ is the M\"obius function.
  \label{thm:primfac}
\end{theorem}
%
%
%\begin{remark}[1]
\begin{remark}
The M\"obius function $\mu(n)$ is $(-1)^k$
  if $n$ is the product of $k$ distinct primes,
  or 0 if $n$ is divisible by a square of a prime.
%Thus,
$\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots,
  from $n = 1$%.
%The $\mu(n)$ is useful for inversion:
%$g(n) = \sum_{d|n} \mu(n/d) \, h(d)$
%if and only if $h(n) = \sum_{d|n} g(d)$
\cite{hardy}.
\end{remark}
%
%
%\begin{remark}[2]
\begin{remark}
%$B_{d,c}\Rlam$ is a polynomial of $\lambda$.
Despite the argument $\lambda^{1/c}$,
  the product $\prod_{k=1}^c A_d(R, e^{2k\pi i/c} \lambda^{1/c})$,
  hence $B_{d,c}\Rlam$,
  is free from radicals of powers of $\lambda^{1/c}$,
  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$.
Thus, $B_{d, c}\Rlam$ is a polynomial of $\lambda$,
and $\deg_\lambda B_{d,c}\Rlam = \deg_\lambda A_d\Rlam$.
Particularly, $B_{n,1}\Rlam = A_n\Rlam$.
\end{remark}
%
%
%We will refer to $P_n\Rlam$ as the \emph{primitive factor} below.
%
%
Let us apply \refeq{primfac}
to some examples in \refsec{examples}.
We will omit the argument $R$ below for convenience.
%%
For $n = 1$,
%there is no irrelevant factor in \refeq{xr1} and
$P_1(\lambda) = B_{1,1}(\lambda) = A_1(\lambda)
  = \lambda^2 - 2\,\lambda - 4\,R$.
%
%
%
For $n = 2$, since
$B_{1,2}(\lambda)
=
A_1(\sqrt{\lambda})
A_1(-\sqrt{\lambda})
=
(4R-\lambda)^2 -4\lambda$,
%
$P_2(\lambda) = A_2(\lambda) \, B_{1,2}(\lambda)^{-1} = 4R - 4 + \lambda$.
%
%
For $n = 4$,
%we have
%$16 (R-1)^2 - \lambda
%= (4R - 4 + \sqrt{\lambda})(4R - 4 - \sqrt{\lambda})$
%and
%$
%(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda
%=
%\big[(4R - \sqrt{\lambda})^2  - 4\sqrt{\lambda}\,\big]
%\big[(4R + \sqrt{\lambda})^2  + 4\sqrt{\lambda}\,\big]$.
%Thus,
we can show that
the last two factors of \refeq{xr4}
can be written as
$B_{2,2}(\lambda) = A_2(\sqrt{\lambda}) A_2(-\sqrt{\lambda})$,
and
%
$P_4(\lambda)
    = A_4(\lambda) \, B_{2,2}(\lambda)^{-1}$
indeed the yields the sextic factor.
%$    = 4096 R^6-12288 R^5+ 256 (\lambda + 48) (R^4- R^3)
%    -16(\lambda + 32)(\lambda - 16) R^2 - (\lambda-16)^3$.
Note, $B_{1,4}(\lambda)$ is unused for $\mu(4) = 0$.
